\begin{abstract}
\indent 
%     In the past few years...
%     Restatement of the problem
%     Assumptions and rationale/justification
%     Model design and justification
%     Model testing and sensitivity analysis
%     Strengths and weaknesses
%     We apply \textbf{LDA topic model} to give an intuitive description of what reviews care about.
    
    As for question 1(a), we first build \textbf{CAFE}, a novel framework for Characterization, Analysis, Forecast and Evaluation on the energy profile (EP) of a state. In a multifaceted manner, the EP is composed of 20 items selected from the 605 variables in the provided data. 
    
    In question 1(b), \textbf{Gaussian Process Regression (GPR)} model is utilized to characterize the evolution of the EP in each state from 1969 to 2009, including the basic evolving trends, the strong fluctuations and the random noise level.
    
    With regard to question 1(c), we combine \textbf{Gray Relational Analysis} and \textbf{Kendall Rank} together in order to analyze the similarities and difference of EPs among states in value and tendency, respectively.
    
    As to question 1(d), the possible influential factors are unveiled after applying both \textbf{Pearson Correlation Coefficient} and \textbf{Partial Relational Coefficient} to the similarity analysis.
    
    In terms of question 1(e), we extract 7 indexes concerning renewable energy and use \textbf{Entropy Weight Method} to illustrate their importance. Further, we make use of \textbf{TOPSIS} method to calculate the comprehensive score of the four states and come to conclusion that California(CA) having the "best" profile.
    
    Regarding question 1(f), we formulate an AMRA-GPR Hybrid model for EP prediction for 2025 and 2050 in a pioneering way, which suits itself to short-term and long-term prediction. Moreover, we propose a sliding window mechanism and a 'Look-Ahead' refinement approach incorporating more information in prediction.
    
    For question 2(a), determine targets.
    
    For question 2(b), propose three actions.
    
    
	\begin{keywords}
	\vspace{5pt}
    Gaussian Process Regression; Gray Relational Analysis; Kendall Rank; Pearson Correlation Coefficient; Partial Relational Coefficient; Entropy Weight Method; TOPSIS; 
	\end{keywords}
\end{abstract}